DENVar: A global Dynamic Estimate of NDVI Variance

### 2025-04-14 writing/manuscript.Rmd
added 2 refs

We represent NDVI using a modified version of Fabio Crameri's divergent *bukavu* palette [@crameri_geodynamic_2018], which has high-contrast for deuteranope and protanope vision. For NDVI values between 0 and 1 (the right half of the palette), the colors also have sufficient contrast for the colors to be distinguishable by both tritanope and achomatic vision. Appendix A contains an approximate representation of the color palette for each vision type. We obtained all color palettes from the `khroma` package [v. 1.14.0, @frerebeau_khroma_2024] for `R` [v. 4.4.1, @r_core_team_r_2024].

@@

* `{khroma}`: @frerebeau_khroma_2024
* @keith_predicting_2008
* @chevin_adaptation_2010
* @rickbeil_plasticity_2019
* @mueller_search_2008
* @pettorelli_using_2005
* @keys_machine-learning_2021
* @nilsen_can_2005
* @stephens_optimal_1982
* @merkle_large_2016
* @tian_evaluating_2015
* @huang_commentary_2021
* @fan_global_2016
* @wang_stochastic_2019
* @pease_ecological_2024
* @xu_plasticity_2021
* @mezzini_how_2025

>>>>

We represent NDVI using a modified version of Fabio Crameri's divergent *bukavu* palette [@crameri_geodynamic_2018; @crameri_misuse_2020], which has high-contrast for deuteranope and protanope vision. For NDVI values between 0 and 1 (the right half of the palette), the colors also have sufficient contrast for the colors to be distinguishable by both tritanope and achomatic vision. Appendix A contains an approximate representation of the color palette for each vision type. We obtained all color palettes from the `khroma` package [v. 1.14.0, @frerebeau_khroma_2024] for `R` [v. 4.4.1, @r_core_team_r_2024].

@@

* `{khroma}`: @frerebeau_khroma_2024
* @keith_predicting_2008
* @chevin_adaptation_2010
* @rickbeil_plasticity_2019
* @mueller_search_2008
* @pettorelli_using_2005
* @keys_machine-learning_2021
* @nilsen_can_2005
* @stephens_optimal_1982
* @merkle_large_2016
* @tian_evaluating_2015
* @huang_commentary_2021
* @fan_global_2016
* @wang_stochastic_2019
* @pease_ecological_2024
* @xu_plasticity_2021
* @mezzini_how_2025
* **TO READ:** Site fidelity as a maladaptive behavior in the Anthropocene: https://esajournals.onlinelibrary.wiley.com/doi/full/10.1002/fee.2456
